Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-11-25 LaTeX_paper/paper.tex
refactor applying sotha soltion to real world

\subsection{Digital vs Real World Puzzles}

@@

This shows how the execution time can be six times faster just by making
each piece more unique.
\subsection{Run to Run Variation}

@@

\subsection{Accuracy}
It is crucial to mention that the project currently lacks an automated
method for evaluating the accuracy of results. However, the accuracy
of two real-world puzzles (4x4 and 8x8) and one digital puzzle (16x16) has been manually confirmed,
with them achieving a 100\% correctness.

\subsection{Answering The Question}

@@

\section{Applying Already Existing Algorithms To The Real World}
With the initial setup completed, it is now possible to
test the existing algorithms with real-world puzzle. For this test,
the fist algorithm~\cref{document:GCL} is selected due to the comprehensive
details provided in the paper. Notably, it contains information
regarding the algorithm's accuracy in relation to the corruption rate,
which is crucial for this analysis.

The conducted tests reveal that the Comparator developed in this paper~\cref{document:my_comparator}
and the ``Graph Connection Laplacian'' solution ~\cref{document:my_comparator} are not compatible with each other.
A formal proof supporting this assertion is presented subsequently.

\subsection{Proof}

The comparison algorithm deceived in section~\cref{document:my_comparator} outputs a compatibility
shore that goes from 0 to 1.\newline
But the algorithm~\cref{document:GCL} takes as input a binary value.
Which means that it is necessary to apply a threshold to the input
data to convert them from float to bool.
\subsubsection{Input Data}
To find the optimal threshold a small 16 piece puzzle has been solved.
And the following 4 values have been measured, in function of the threshold:

>>>>

\subsubsection{Digital vs Real World Puzzles}

@@

This shows how the execution time can be six times faster just by making
each piece more unique.
\subsubsection{Run to Run Variation}

@@

\subsubsection{Accuracy}
It is crucial to mention that the project currently lacks an automated
method for evaluating the accuracy of results. However, the accuracy
of two real-world puzzles (4x4 and 8x8) and one digital puzzle (16x16) has been manually confirmed,
with them achieving a 100\% correctness.

\subsubsection{Answering The Question}

@@

Comparing the results achieved by our algorithm with some of the algorithms seen in the related
work section (\cref{document:related_work}), clearly shows how our algorithm is far away
from the current state of the art digital puzzle solvers. In this section we want to
see if it is possible to use our comparator with current state of the art algorithms.
In particular we selected the ``Graph Connection Laplacian'' solution, due to the
comprehensive details provided in the paper. Notably, it contains information
regarding the algorithm's accuracy in relation to the corruption rate,
which is crucial for this analysis.

Unfortunately the conducted tests reveal that the Comparator developed
in this paper~\cref{document:my_comparator}
and the ``Graph Connection Laplacian'' solution~\cref{document:GCL}
are not compatible with each other.
A formal proof supporting this assertion is presented subsequently.

\subsubsection{Selecting The Threshold Based On Input Data}

The comparison algorithm deceived in section~\cref{document:my_comparator} outputs a compatibility
shore that goes from 0 to 1.\newline
But the algorithm~\cref{document:GCL} takes as input a binary value.
Which means that it is necessary to apply a threshold to the input
data to convert them from float to bool.

To find the optimal threshold a small 16 piece puzzle has been solved.
And the following 4 values have been measured, in function of the threshold:
